Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-03-01 writeup/gz_hubble_data.tex
added paragraph about redshifts to writeup and added figure comparing speczs from Griffith 3dhst and MUSYC catalogs

We obtain redshifts from a variety of sources: spectroscopic and photometric redshifts from \citet{gri12}, spectroscopic, photometric, and grism redshifts from 3DHST \citep{mom15}, and photometric redshifts from UltraVISTA \citep{ilb13}. The distribution is shown in Table~\ref{redshifts}, and are located in the `$\rm Z~BEST$' column of the catalog. We first use the \citep{gri12} and \citep{mom15} redshifts if those are available. If they are not, then we compare the 1$\sigma$ errors of the photometric and grism redshits from all three catalogs, and use the redshift with the smallest error. The source of the redshifts are displayed in the $\rm Z~BEST~SOURCE$ column of the catalog.

\begin{table*}
\caption{Redshift sources of the Hubble data, by sample.  \label{redshifts}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                  & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S & GOODS FULL    & SDSS    & Total \\
\hline
Griffith specz                  & 3,656    & 7,201  & 387   & 1,997  & 3,016   &           	&         & 16,257\\
3DHST specz                      & 12       & 35     & 6     & 5      & 103     &               &         & 161\\
Griffith photoz                 & 4,442    & 82,662 & 8,886 & 218    & 1,662   &               &         & 97,870\\ 
3DHST grismz                     & 341      & 358    & 9     & 101    & 67      &               &         & 876\\
UltraVista photoz                & 0        & 2,473  & 0     & 0      & 0       &           	&         & 2,473\\
3DHST photoz                     & 56       & 79     & 16    & 230    & 65      &           	&         & 446\\

Total                            & 8,507    & 92,808 & 9,304 & 2,551  & 4,913   & 11,157    	& 51,861  & 181,101\\
\hline\hline
\end{tabular}
\end{table*}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable}{lrrllcrrrrrr|c}
\rotate
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications} 
\label{tab:catalog}
\tabletypesize{\scriptsize}
\tablehead{
 &  &   &  &  
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\dots$}
\\
\colhead{OBJNO} & 
\colhead{RA} & 
\colhead{DEC} & 
\colhead{Imaging} & 
\colhead{Correctable Category} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{best} &
\colhead{}
}
\small
\startdata
10000034            & 188.93       & 62.23         & AEGIS           &  correctable &  72 &  10 &  10.0 & 0.625 & 0.625 & 0.629 & 0 \\
10000162            & 160.99      & 11.70          & AEGIS           &  uncorrectable &  84 &  17 &  17.0 & 0.810 & 0.810 & 0.810 & 1 \\
5001356             & 210.80       & 54.15         & GOODS-N-Shallow &  correctable &  88 &  18 &  18.0 & 0.783 & 0.783 & 0.722 & 0 \\
9003947835          & 176.54       & 8.74          & GOODS-S-Shallow &  nei &  48 &  16 &  16.0 & 1.000 & 1.000 & 1.000 & 1 \\
GDS~S~16203         & 186.44       & 47.88         & GOODS-FULL      &  nei &  89 &  17 &  17.0 & 0.739 & 0.739 & 0.739 & 0 \\
8647474690312438284 & 188.93       & 62.64         & SDSS            &  zlt3 &  91 &   0 &   0.0 & 0.000 & 0.000 & 0.000 & 0 \\
20061690            & 160.99       & 11.70         & COSMOS          &  nei &  65 &   4 &   3.4 & 0.333 & 0.295 & 0.295 & 0 \\
20061692            & 176.54       & 8.45          & COSMOS          &  correctable &  75 &  14 &  14.0 & 0.609 & 0.629 & 0.666 & 0 \\
90022947            & 230.24       & 84.20         & GEMS           &  zlt3 & 129 &  12 &  12.0 & 0.462 & 0.462 & 0.492 & 0 \\
20063829            & 203.23       & 93.20         & COSMOS         &  correctable &  69 &  18 &  17.0 & 0.900 & 0.895 & 0.840 & 1 \\
\enddata
\tablecomments{Full version is online at some website, here are 10 rows out of 181,101 in the full version.\emph{These numbers are super fake right now - put real values in for final version!}}
\end{deluxetable}

>>>>

We compiled redshifts from a variety of sources to include in the GZH catalog. For each galaxy, the redshift selected is in the $\tt Z\_Best$ column of the data (see Table~\ref{tab:catalog}), its type (spectroscopic: $\tt SPEC\_Z$, photometric: $\tt PHOTO\_Z$, or grism: $ \tt GRISM\_Z$) is listed in the column $\tt Z\_BEST\_TYPE$, and the source catalog ($\tt Griffith$ \citep{gri12}, $\tt 3DHST$ \citep{mom15}, $\tt MUSYC$ \citep{car10}, or $\tt UltraVISTA$ \citep{ilb13}) of the redshift is in column $\tt Z\_BEST\_SOURCE$.

For galaxies which have redshifts from multiple sources, we use the following algorithm to select the $\tt Z\_BEST$ redshift. We first prioritize spectroscopic redshifts; these are provided in the Griffith, 3DHST, and MUSYC catalogs. If a high quality spec-z exists in the Griffith catalog we use that, else 3DHST, else MUSYC. We show in Figure~\ref{fig:speczs} that over 98\% of the the spec-z's are consistent with each other, and therefore the priority order of selection makes no negligible difference. If no spectroscipic redshifts are available, we compare the 1-$\sigma$ errors of the photometric (Griffith, 3DHST, MUSYC, UltraVISTA) and grism (UltraVISTA) redshifts, and use the redshift with the smallest error. Table~\ref{tab:redshifts} shows the results of this selection.

\begin{figure*}
\includegraphics[width=160mm]{figures/specz_comparison.pdf}
\caption{Spectroscopic redshifts from Griffith, 3DHST, and MUSYC catalogs. The number in the upper left of each plot is the percentage of redshifts which agree within $\Delta z < 0.05$ between the two catalogs being compared in each panel. Within this range there is over 98\% agreement in redshifts between all three catalogs.}
\label{fig:speczs}
\end{figure*}

\tabletypesize{\scriptsize}
\begin{deluxetable}{l|rr|rrr|rr|r|rr}
\centering
%\rotate
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH redshifts by survey} 
\label{tab:redshifts}
\tabletypesize{\scriptsize}
\tablehead{
 &   
\multicolumn{2}{c}{\underline{Griffith}} &
\multicolumn{3}{c}{\underline{3DHST}} &
\multicolumn{2}{c}{\underline{MUSYC}} &
\multicolumn{1}{c}{\underline{UltraVISTA}}&
\multicolumn{2}{c}{\underline{Total}} 
\\
\colhead{Survey} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{grism-z} & 
\colhead{photo-z} & 
\colhead{spec-z} & 
\colhead{photo-z} & 
\colhead{photo-z} & 
\colhead{with redshift} &
\colhead{in survey}
}
\small
\startdata
%Survey     Gs        Gp    3ds    3dg     3dp       Ms      Mp       UVp       total
AEGIS    & 3,656  & 2,941  & 12  &  515  &  249    & 0     & 0     &  0      & 7,373  & 8,507\\
COSMOS   & 7,201  & 77,435 & 35  &  358  &  26     & 0     & 0     &  2,665  & 85,020 & 92,808 \\
GEMS     & 387    & 628    & 6   &  99   &  40     & 279   & 7,304 & 0       & 8,743  & 9,304\\
GOODS-N  & 1,947  & 37     & 418 & 1,545 &  1,381  & 0     & 0     & 0       & 5,328  & 12,030 \\
GOODS-S  & 1,080  & 4      & 327 & 1,348 &  281    & 816   & 1,184 & 0       & 5,040  & 10,284 \\
SDSS     & 0      & 0      & 0   &  0    &  0      & 0     & 0     & 0       & 37,545 & 51,861  \\
\hline
Total    & 14,271 & 81,045 & 798 & 3,865 & 1,977   & 1,095 & 8,488 & 2,665   & 114,204 & 184,794\\
\enddata
\end{deluxetable}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable}{lrrllcrrrrrr|c}
\centering
%\rotate
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications} 
\label{tab:catalog}
\tabletypesize{\scriptsize}
\tablehead{
 &  &   &  &  
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\dots$}
\\
\colhead{OBJNO} & 
\colhead{RA} & 
\colhead{DEC} & 
\colhead{Imaging} & 
\colhead{Correctable Category} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{best} &
\colhead{}
}
\small
\startdata
10000034            & 188.93       & 62.23         & AEGIS           &  correctable &  72 &  10 &  10.0 & 0.625 & 0.625 & 0.629 & 0 \\
10000162            & 160.99      & 11.70          & AEGIS           &  uncorrectable &  84 &  17 &  17.0 & 0.810 & 0.810 & 0.810 & 1 \\
5001356             & 210.80       & 54.15         & GOODS-N-Shallow &  correctable &  88 &  18 &  18.0 & 0.783 & 0.783 & 0.722 & 0 \\
9003947835          & 176.54       & 8.74          & GOODS-S-Shallow &  nei &  48 &  16 &  16.0 & 1.000 & 1.000 & 1.000 & 1 \\
GDS~S~16203         & 186.44       & 47.88         & GOODS-FULL      &  nei &  89 &  17 &  17.0 & 0.739 & 0.739 & 0.739 & 0 \\
8647474690312438284 & 188.93       & 62.64         & SDSS            &  zlt3 &  91 &   0 &   0.0 & 0.000 & 0.000 & 0.000 & 0 \\
20061690            & 160.99       & 11.70         & COSMOS          &  nei &  65 &   4 &   3.4 & 0.333 & 0.295 & 0.295 & 0 \\
20061692            & 176.54       & 8.45          & COSMOS          &  correctable &  75 &  14 &  14.0 & 0.609 & 0.629 & 0.666 & 0 \\
90022947            & 230.24       & 84.20         & GEMS           &  zlt3 & 129 &  12 &  12.0 & 0.462 & 0.462 & 0.492 & 0 \\
20063829            & 203.23       & 93.20         & COSMOS         &  correctable &  69 &  18 &  17.0 & 0.900 & 0.895 & 0.840 & 1 \\
\enddata
\tablecomments{Full version is online at some website, here are 10 rows out of 181,101 in the full version.\emph{These numbers are super fake right now - put real values in for final version!}}
\end{deluxetable}
